Elephant Seal Age JAE Intraspecific Variation

### 2023-12-08 paper/paperv3.qmd
Updating supplemental tables

```{r}
#| label: fig-repro_age
#| fig-cap: "Pup survival and recruitment are not significantly affected by maternal age. Points are mean values for maternal age. Error bars show SE."
#| fig-width: 4.5

@@

@@

```{r}
surv_mod_summary <- summary(pup_surv_model)
surv_mod_kable <- surv_mod_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)", "Age (quadratic)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`, digits = 2),
         Response = "Survival") %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Response, Parameter)

@@

rbind(surv_mod_kable, recruit_mod_kable) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::collapse_rows(columns = 1)
```

Supplemental figure for survival bias:

```{r}
#| label: fig-surv_bias
#| fig-cap: "A: Plotting the intercept of the random effect of year shows that variation in ocean conditions is likely driving patterns in survival, rather than age of mother. B: 95% of seals that survived were resighted within ~seven years of their birth."
#| fig-width: 9

year_ranef <- ranef(pup_surv_model)$year %>% 
  as_tibble(rownames = "year") %>% 
  mutate(year = as.numeric(year)) %>% 
  rename(intercept = `(Intercept)`)

year_ranef_plot <- ggplot(year_ranef, aes(year, intercept)) + 
  geom_point() + 
  geom_smooth(method = "loess", 
              formula = y ~ x,
              color = "red") + 
  theme_classic()

survival_bias <- sealdat %>% 
  group_by(animalID) %>% 
  summarize(first_resight_yrs = min(age))

survival95 <- quantile(survival_bias$first_resight_yrs, 0.95)
#n for 95% quantile
sum(survival_bias$first_resight_yrs > 7)

survival_bias_plot <- ggplot(survival_bias, aes(x = first_resight_yrs)) +
  stat_ecdf() +
  geom_vline(xintercept = survival95, linetype = "dashed", color = "red") +
  scale_x_continuous(limits = c(0, 10)) + 
  theme_classic()

plot_grid(year_ranef_plot, survival_bias_plot, nrow = 1, labels = "AUTO")
```

@@

```{r}
pupsex_mod_summary <- summary(pup_sex_mod)
pupsex_mod_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`/2, digits = 3)) %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Parameter) %>% 
  knitr::kable()

>>>>

```{r}
#| label: fig-repro_age
#| fig-cap: "Pup survival and recruitment are not significantly affected by maternal age. Points are mean values for maternal age. Error bars show SE."
#| fig-width: 5.5

@@

```{r}
#| label: tbl-survrecruit-cap

surv_recruit_cap <- str_glue("The results from offspring survival and recruitment analyses. In the offspring survival model, the random effect variance of animal id is {format_signif(VarCorr(pup_surv_model)$animalID, 3)} and of year was {format_signif(VarCorr(pup_surv_model)$year, 3)}. In the offspring recruitment model, the random effect variance of animal id is {format_signif(VarCorr(pup_recruit_model)$animalID, 3)} and of year was {format_signif(VarCorr(pup_recruit_model)$year, 3)}")

@@

```{r}
#| tbl-cap: !expr "surv_recruit_cap"
#| label: tbl-surv_recruit

surv_mod_summary <- summary(pup_surv_model)
surv_mod_kable <- surv_mod_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)", "Age (quadratic)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`, digits = 2),
         Response = "Survival") %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Response, Parameter)

@@

rbind(surv_mod_kable, recruit_mod_kable) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::collapse_rows(columns = 1)

@@

```{r}
#| label: tbl-pupsex-cap

pupsex_cap <- str_glue("The results from offspring sex ratio analyses. In the model, the random effect variance of animal id is {format_signif(VarCorr(pup_sex_mod)$animalID, 3)} and of year was {format_signif(VarCorr(pup_sex_mod)$year, 3)}. 
```

```{r}
#| label: tbl-pupsex
#| tbl-cap: !expr "pupsex_cap"

pupsex_mod_summary <- summary(pup_sex_mod)
pupsex_mod_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `z value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|z|)`/2, digits = 3)) %>%
  select(-`Pr(>|z|)`) %>% 
  relocate(Parameter) %>% 
  knitr::kable()
